### 2015-05-18 Harris_2015/three_species.Rmd
minor fixes for three_species

Not

```{r}
Pairs.txt = readLines("fakedata/three/Pairs.txt")
z_score_column = grep("Z-Score", Pairs.txt, value = TRUE)[2] %>% 
  strsplit(" +") %>% 
  extract2(1) %>% 
  grep("Z-Score", .)

# A success for Pairs.exe implies Z>0 because C-scores are about absences, not presences

pairs_evaluation = Pairs.txt[grep("(Var2.*Var1)|(Var1.*Var2)", Pairs.txt)] %>% 
    strsplit(" +") %>%
    sapply(. %>% extract(z_score_column) %>% as.numeric) %>%
    is_greater_than(0)
```

>>>>

```{r}
Pairs.txt = readLines("fakedata/three/Pairs.txt")

# Find the column that contains the Z-score
z_score_column = grep("Z-Score", Pairs.txt, value = TRUE)[2] %>% 
  strsplit(" +") %>% 
  extract2(1) %>% 
  grep("Z-Score", .)

# Find the right rows of the text file, split them on whitespace, pull out
# the column identified above, and find its sign
pairs_evaluation = Pairs.txt[grep("(Var2.*Var1)|(Var1.*Var2)", Pairs.txt)] %>% 
    strsplit(" +") %>%
    sapply(. %>% extract(z_score_column) %>% as.numeric) %>%
    is_greater_than(0) # Z>0 implies negative interactions because the Z-score
                       # relates to the distribution of C-scores, which describe
                       # the frequency with which species *do not* co-occur
```
